intro

### 2022-03-16 06_Paper/ER-ED/TheoreticalBackground.Rmd
Update TheoreticalBackground.Rmd
Update EMG Teil

Psychophysiology provides further important information on the effectiveness of emotion regulation strategies.
Compared to cardiovascular, electrodermal, and pupillometric autonomic responses, facial electromoygraphy has been reported consistently across studies to be influenced by emotion regluation with even medium effect sizes [@Zaehringer2020].
For example, studies have shown that reappraisal of negative emotion is associated with reduced activity of the Corrugtor muscle (associated with anger, sadness, and fear) and the levator muscle (associated with disgust) with _d~-~_ = 0.32 ([@Zaehringer2020]) and _d~-~_ = XXX (XXX), respectively. 
Similar effects have been reported for suppression (XXX) and distancing/distraction (XXX).

einführen als Valenz: hier und/oder weiter unten!!!
test von heute

@@

The aim of the present study is to evaluate whether this paradigm is suitable for determining SVs of ER strategies. 
As a manipulation check, we first want to investigate whether the valence (neutral, negative) of the pictures is effecting subjective and physiological responding (EMG).
Second, we want to check whether the ER strategies distraction, distancing, and suppression effectively reduce subjective and physiological responding as well as, third, whether they require cognitive effort. 
The following hypotheses are proposed:
<!-- es gibt bisher noch keine Begründnung/Einbettung der nachfolgenden Hypothesen. Z.B.: Warum wird Corrugator und Levator untersucht? m.E. müsste oben jeweils noch ein Satz ergänzt werden, warum genau diese Variable in der aktuellen Studie untersucht werden soll.--> <!-- Denise: ja, das hab ich auch bemerkt, ist EMG auch arousal? Dann dies erstens noch einführen und argumentieren und dann auch als physiological arousal aufführen. oder steht corrugator für arousal und levator für valence? dann auch so benennen. Außerdem subjective arousal/ subjective effort auch immer konsistent benennen. Ich schlage vor hier in den hypothesen immer von subjective arousal / effort zu sprechen, dies dann im Methodenteil über die subjective ratings / effort ratings zu operationalisieren (fehlt übrigens im Methodenteil noch.-->
<!-- Denise: im analysis plan habt ihr auch den vergleich negative vs. neutral (active viewing) beschrieben, deshalb hab ich das hier mal als Hypothese aufgenommen-->
<!-- Anne: Ich habe jetzt Corrugator und Levator mal zusammengefasst-->

>>>>

Psychophysiological measures provide further important information on the effectiveness of emotion regulation strategies (for an overview, see [@Zaehringer2020]).
Compared to cardiovascular, electrodermal, and pupillometric autonomic responses, facial electromyography has been reported consistently across studies to be influenced by emotion regulation with even medium effect sizes.
For example, studies have shown that reappraisal of negative emotion is associated with reduced activity of the corrugator supercilii (associated with anger, sadness, and fear) with _d~-~_ = 0.32 ([@Zaehringer2020]).
In addition, the levator labii superioris (associated with disgust) has also been associated with reduced activity during reappraisal (Burr et al., 2021; https://doi.org/10.1371/journal.pone.0247246). 
Similar effects have been reported for suppression (Burr et al., 2021), distancing (Gärtner et al., 2021), and distraction (Schönfelder et al., 2014 DOI: 10.1093/scan/nst116).
Importantly, results on electromyographic measures  seem to be more consistent compared to other autonomic measures, likely because they are specific to emotional valence and its changes.
<!-- Anne: please add references-->

@@

The aim of the present study is to evaluate whether this paradigm is suitable for determining SVs of ER strategies. 
As a manipulation check, we first want to investigate whether the valence of the pictures (neutral, negative) is effecting subjective and physiological responding (EMG).
Second, we want to check whether the ER strategies distraction, distancing, and suppression effectively reduce subjective and physiological responding as well as, third, whether they require cognitive effort. 
The following hypotheses are proposed:
<!-- es gibt bisher noch keine Begründnung/Einbettung der nachfolgenden Hypothesen. Z.B.: Warum wird Corrugator und Levator untersucht? m.E. müsste oben jeweils noch ein Satz ergänzt werden, warum genau diese Variable in der aktuellen Studie untersucht werden soll.--> 
<!-- Denise: ja, das hab ich auch bemerkt, ist EMG auch arousal? Dann dies erstens noch einführen und argumentieren und dann auch als physiological arousal aufführen. oder steht corrugator für arousal und levator für valence? dann auch so benennen. Außerdem subjective arousal/ subjective effort auch immer konsistent benennen. Ich schlage vor hier in den hypothesen immer von subjective arousal / effort zu sprechen, dies dann im Methodenteil über die subjective ratings / effort ratings zu operationalisieren (fehlt übrigens im Methodenteil noch.-->
<!-- Denise: im analysis plan habt ihr auch den vergleich negative vs. neutral (active viewing) beschrieben, deshalb hab ich das hier mal als Hypothese aufgenommen-->
<!-- Anne: Ich habe jetzt Corrugator und Levator mal zusammengefasst. Ich habe noch keine ausführliche Begründung fürs EMG eingefügt =  würde ich nur machen, wenn das für die anderen Maße auch geplant ist, sonst sieht es m.E. komisch aus.-->
